\documentclass[sigconf]{acmart}

\setcopyright{acmlicensed}
\copyrightyear{2026}
\acmYear{2026}
\acmDOI{XXXXXXX.XXXXXXX}

\acmConference[SIGGRAPH Asia 2026]{ACM SIGGRAPH Asia 2026 Posters}{December 2026}{Tokyo, Japan}
\acmISBN{XXX-X-XXXX-XXXX-X/26/12}

\begin{document}

\title{Hammerhead HMD: An Underwater Augmented Reality Headset with Cephalophoil-Inspired Design}

\author{Sho Nakazawa}
\affiliation{%
  \institution{University of Tsukuba}
  \city{Tsukuba}
  \country{Japan}
}
\email{shonkzw0927@gmail.com}

\begin{abstract}
We present Hammerhead HMD, an underwater augmented reality head-mounted display inspired by the cephalophoil morphology of hammerhead sharks.
The device is designed to enhance spatial perception and information overlay in subaquatic environments.
We evaluate the hydrodynamic performance of the device using Particle Image Velocimetry (PIV) in a water tunnel, demonstrating minimal flow disturbance.
\end{abstract}

\keywords{underwater AR, head-mounted display, hydrodynamics, PIV, augmented reality}

\maketitle

\section{Introduction}

Augmented reality in underwater environments presents unique engineering challenges including optical distortion, pressure resistance, and hydrodynamic drag.
We propose the Hammerhead HMD, a cephalophoil-shaped underwater AR headset designed to address these challenges.
The distinctive cephalophoil geometry, inspired by hammerhead sharks, provides improved lateral field of view while reducing hydrodynamic resistance.

\section{System Design}

\subsection{Optical Design}
[Describe the optical system here]

\subsection{Structural Design}
The housing adopts a cephalophoil morphology, extending laterally to house wide-baseline cameras and displays.
This geometry distributes optical elements similarly to the eye placement of hammerhead sharks, enhancing stereoscopic depth perception underwater.

\section{Hydrodynamic Evaluation}

We evaluate the device using Particle Image Velocimetry (PIV) in a water tunnel facility.
PIV allows quantitative visualization of the flow field around the HMD, enabling measurement of drag and turbulence characteristics.

\subsection{Experimental Setup}
[Describe PIV setup and water tunnel parameters]

\subsection{Results}
[Present PIV results and flow visualization]

\section{Conclusion}

We presented the Hammerhead HMD, an underwater AR headset with a cephalophoil-inspired design.
PIV evaluation confirms [results].
Future work includes [next steps].

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
